Machine Learning Tools for Open Cluster Characterization with Gaia DR2 Data

### 2021-02-10 thesis/thesis.tex

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Open Cluster} & \emph{$\alpha$ J2000 $(degrees)$} & \emph{$\delta$ J2000 $(degrees)$} & \emph{Radius $(arcmin)$} & \emph{\# stars} \\
      \hline
      NGC 2516 & 119.517 & -60.753 & 15 & 12,869 \\
      NGC 2632 & 130.1 & 19.667 & 35 & 13,167 \\
      NGC 2682 & 132.825 & 11.8 & 12.5 & 2,839 \\
      Melotte 22 & 56.75 & 24.117 & 60 & 61,552 \\
      Melotte 25 & 66.725 & 15.867 & 165 & 433,996 \\
    \end{tabular}
    \caption{Righ ascension, declination, radius and number of stars of studied clusters.
             The number of stars corresponds to those stars contained within a cone of center
             $(\alpha, \delta)$ and raius the cluster's radius multiplied by a factor of 1.5.}
    \label{tab:clusters_summary}
  \end{center}
\end{table}

>>>>

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Open Cluster} & \emph{$\alpha$ J2000 $(degrees)$} & \emph{$\delta$ J2000 $(degrees)$} & \emph{Radius $(arcmin)$} & \emph{\# stars} \\
      \hline
      NGC 2516 & 119.517 & -60.753 & 15 & 12,869 \\
      NGC 2632 & 130.1 & 19.667 & 35 & 13,167 \\
      NGC 2682 & 132.825 & 11.8 & 12.5 & 2,839 \\
      Melotte 22 & 56.75 & 24.117 & 60 & 61,552 \\
      Melotte 25 & 66.725 & 15.867 & 165 & 433,996 \\
    \end{tabular}
    \caption{Right ascension, declination, radius and number of stars of studied clusters.
             The number of stars corresponds to those stars contained within a cone of center
             \((\alpha, \delta)\) and radius the cluster's radius multiplied by a factor of 1.5.}
    \label{tab:clusters_summary}
  \end{center}
\end{table}
